Generating Random Logic Programs Using Constraint Programming

### 2020-06-02 text/paper2/paper.tex
Un-anonymise

\title{Generating Random Logic Programs Using Constraint Programming}
%\author{Paulius Dilkas\inst{1} \and
%Vaishak Belle\inst{1,2}}
%\authorrunning{P. Dilkas and V. Belle}
%\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}

@@

%\subsubsection*{Acknowledgments.}
%This work was supported by the EPSRC Centre for Doctoral Training in Robotics
%and Autonomous Systems, funded by the UK Engineering and Physical Sciences
%Research Council (grant EP/S023208/1).

>>>>

\title{Generating Random Logic Programs Using Constraint Programming}
\author{Paulius Dilkas\inst{1} \and
Vaishak Belle\inst{1,2}}
\authorrunning{P. Dilkas and V. Belle}
\institute{University of Edinburgh, Edinburgh, UK \email{\{p.dilkas@sms.,vaishak@\}ed.ac.uk} \and Alan Turing Institute, London, UK}

@@

\subsubsection*{Acknowledgments.}
This work was supported by the EPSRC Centre for Doctoral Training in Robotics
and Autonomous Systems, funded by the UK Engineering and Physical Sciences
Research Council (grant EP/S023208/1).
